Time Series Bootstrapping For Solar Current

### 2021-12-17 deliverables/paper.Rmd
Added units and clarification

The model paper for this project, @miozzo_2014
used data cited from the NSRDB.
However,
there were some discrepancies between our data
and the data used in @miozzo_2014.
Firstly, the year range in the paper was 1991--2010,
while the year range available when we acquired
the data from the NSRDB API was 1998--2010.
Secondly, the primary variable used in
was extraterrestrial radiation,
"the amount of global horizontal radiation that a location on Earth would
receive if there was no atmosphere" (@nrel_glossary).
Our primary measure was global horizontal radiation (GHI),
which is the total solar radiation to reach
a horizontal plane on the Earth's surface (@nrel_glossary).
Because ETR and GHI are closely related,
we felt that the data was acceptable for a
replication of the process in @miozzo_2014,
with the caveat that the calculations may only be approximate.

@@

time_series_ghi <- time_series_of_var(df, "GHI", "GHI", 6)
time_series_power <- time_series_of_var(df, "power_out", "Output power", 6)
ggsave("./images/time_series_ghi.png", make_plot_for_pres(time_series_ghi))
ggsave("./images/time_series_power.png", make_plot_for_pres(time_series_power))
```

@@

hour_plot_ghi <- hour_plot_of_var(df, "GHI", "GHI")
hour_plot_power <- hour_plot_of_var(df, "power_out", "Output Power")
ggsave("./images/hour_plot_ghi.png", make_plot_for_pres(hour_plot_ghi))
ggsave("./images/hour_plot_power.png", make_plot_for_pres(hour_plot_power))
```

@@

```{r unfiltered-hist, fig.cap = "Distribution of power outputs before filtering low-irradiance hours.", echo=FALSE, warning=FALSE}
unfiltered_power_hist <- ggplot() +
  geom_histogram(aes(x = df$power_out, y = ..density..), bins=50) +
  theme_bw() +
  labs(
    x = "Power Output", y = "Density"
  )
print(unfiltered_power_hist)
```

```{r filtered-hist, fig.cap = "Distribution of power outputs after filtering low-irradiance hours.", echo=FALSE, warning=FALSE}
filtered_power_hist <- ggplot() +
  geom_histogram(aes(x = df_high_irradiance$power_out, y = ..density..), bins=50) +
  theme_bw() +
  labs(
    x = "Power Output", y = "Density"
  )
print(filtered_power_hist)
```

@@

sixhr_plot_power <- time_series_irradiance(df_high_irradiance, "power_out", "Power Output", 6)
ggsave("./images/sixhr_plot_power.png", make_plot_for_pres(sixhr_plot_power))

twelvehr_plot_power <- time_series_irradiance(df_high_irradiance, "power_out", "Power Output", 12)
ggsave("./images/twelvehr_plot_power.png", make_plot_for_pres(twelvehr_plot_power))

day_plot_power <- time_series_irradiance(df, "power_out", "Power Output", 24)
ggsave("./images/day_plot_power.png", make_plot_for_pres(day_plot_power))
```

>>>>

The model paper for this project, @miozzo_2014
used data cited from the NSRDB.
However,
there were some discrepancies between our data
and the data used in @miozzo_2014.
Firstly, the year range in the paper was 1991--2010,
while the year range available when we acquired
the data from the NSRDB API was 1998--2010.
Secondly, the primary variable used in
was extraterrestrial radiation,
"the amount of global horizontal radiation that a location on Earth would
receive if there was no atmosphere" (@nrel_glossary).
Our primary measure was global horizontal radiation (GHI),
which is the total solar radiation to reach
a horizontal plane on the Earth's surface (@nrel_glossary).
Because ETR and GHI are closely related,
we felt that the data was acceptable for a
replication of the process in @miozzo_2014,
with the caveat that the calculations may only be approximate.
GHI is measured in units of $W/m^2$, that is,
power per unit area provided by solar radiation.

@@

time_series_ghi <- time_series_of_var(df, "GHI", "GHI (W/m^2)", 6)
time_series_power <- time_series_of_var(df, "power_out", "Output power (W)", 6)
ggsave("./images/time_series_ghi.png", make_plot_for_pres(time_series_ghi))
ggsave("./images/time_series_power.png", make_plot_for_pres(time_series_power))
```

@@

hour_plot_ghi <- hour_plot_of_var(df, "GHI", "GHI (W/m^2)")
hour_plot_power <- hour_plot_of_var(df, "power_out", "Output Power (W)")
ggsave("./images/hour_plot_ghi.png", make_plot_for_pres(hour_plot_ghi))
ggsave("./images/hour_plot_power.png", make_plot_for_pres(hour_plot_power))
```

@@

```{r unfiltered-hist, fig.cap = "Distribution of power outputs before filtering low-irradiance hours.", echo=FALSE, warning=FALSE}
unfiltered_power_hist <- ggplot() +
  geom_histogram(aes(x = df$power_out, y = ..density..), bins=50) +
  theme_bw() +
  labs(
    x = "Power Output (W)", y = "Density"
  )
print(unfiltered_power_hist)
```

```{r filtered-hist, fig.cap = "Distribution of power outputs after filtering low-irradiance hours.", echo=FALSE, warning=FALSE}
filtered_power_hist <- ggplot() +
  geom_histogram(aes(x = df_high_irradiance$power_out, y = ..density..), bins=50) +
  theme_bw() +
  labs(
    x = "Power Output (W)", y = "Density"
  )
print(filtered_power_hist)
```

@@

sixhr_plot_power <- time_series_irradiance(df_high_irradiance, "power_out", "Power Output (W)", 6)
ggsave("./images/sixhr_plot_power.png", make_plot_for_pres(sixhr_plot_power))

twelvehr_plot_power <- time_series_irradiance(df_high_irradiance, "power_out", "Power Output (W)", 12)
ggsave("./images/twelvehr_plot_power.png", make_plot_for_pres(twelvehr_plot_power))

day_plot_power <- time_series_irradiance(df, "power_out", "Power Output (W)", 24)
ggsave("./images/day_plot_power.png", make_plot_for_pres(day_plot_power))
```
